No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System

### 2019-02-13 ms.tex
correct rmoon

Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 29.9$. Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.  %This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.

>>>>

Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 29.9$. Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.

The moon model also yields qualitatively different posterior distributions for the two data sets.  As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$. By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.
